Paper Figures and Text

### 2025-08-22 Fish Data Analysis/Paper_Figures.qmd
Small updates

group_still <- ggplot(group_sum_data %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "),
           y = count,
           fill = Groups)) + 
    geom_bar(position="fill", stat="identity")+
    xlab("") +
    ylab("Proportion of Time") +
    theme_light()+ 
    scale_fill_manual(values=c("8" = "#1D3557","7" = "#325A7C","6" = "#457B9D","5" = "#7BAFBF",
                               "4" = "#A8DADC","3" = "#D0EBE6","2" = "#F1FAEE","1" = "#3ae639")) +
    geom_text(aes(label = sig_letters, y = 1.1), color = "black", size = sig_text_size) +
    theme(axis.text.x = element_text(size = text_size),
          axis.text.y = element_text(size = text_size),
          axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

@@

group_flow <- ggplot(group_sum_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = interaction(Ablation,Darkness,sep=", "),
           y = count,
           fill = Groups)) + 
    geom_bar(position="fill", stat="identity")+
    xlab("") +
    ylab("Proportion of Time") +
    theme_light()+ 
    scale_fill_manual(values=c("8" = "#1D3557","7" = "#325A7C","6" = "#457B9D","5" = "#7BAFBF",
                               "4" = "#A8DADC","3" = "#D0EBE6","2" = "#F1FAEE","1" = "#3ae639")) +
    geom_text(aes(label = sig_letters, y = 1.1), color = "black", size = sig_text_size) +
    theme(axis.text.x = element_text(size = text_size),
          axis.text.y = element_text(size = text_size),
          axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

>>>>

group_still <- ggplot(group_sum_data %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "),
           y = count,
           fill = Groups)) + 
    geom_bar(position="fill", stat="identity")+
    xlab("") +
    ylab("Proportion of Time") +
    theme_light()+ 
    scale_y_continuous(breaks = seq(0, 1, by = 0.25)) +
    scale_fill_manual(values=c("8" = "#1D3557","7" = "#325A7C","6" = "#457B9D","5" = "#7BAFBF",
                               "4" = "#A8DADC","3" = "#D0EBE6","2" = "#F1FAEE","1" = "#3ae639")) +
    geom_text(aes(label = sig_letters, y = 1.1), color = "black", size = sig_text_size) +
    theme(axis.text.x = element_text(size = text_size),
          axis.text.y = element_text(size = text_size),
          axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

@@

group_flow <- ggplot(group_sum_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = interaction(Ablation,Darkness,sep=", "),
           y = count,
           fill = Groups)) + 
    geom_bar(position="fill", stat="identity")+
    xlab("") +
    ylab("Proportion of Time") +
    theme_light()+ 
    scale_y_continuous(breaks = seq(0, 1, by = 0.25)) +
    scale_fill_manual(values=c("8" = "#1D3557","7" = "#325A7C","6" = "#457B9D","5" = "#7BAFBF",
                               "4" = "#A8DADC","3" = "#D0EBE6","2" = "#F1FAEE","1" = "#3ae639")) +
    geom_text(aes(label = sig_letters, y = 1.1), color = "black", size = sig_text_size) +
    theme(axis.text.x = element_text(size = text_size),
          axis.text.y = element_text(size = text_size),
          axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})
